\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{RAFID RAHMAN} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+88 01568202975 \\ Dhaka, BD} 
\address{\href{mailto:rafid0001@gmail.com}{rafid0001@gmail.com} \\ \href{https://www.linkedin.com/in/rafidrahman1}{Linkedin} \\ \href{https://github.com/rafidrahman1}{Git}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

I’m a Fullstack Developer with hands-on experience in building dynamic, scalable applications using React, Next.js, Spring Boot, and Flutter. I’ve contributed to production-ready projects involving AI agent development and Meta Graph API integration. With a Computer Science degree from BRAC University and a strong foundation in both frontend and backend technologies, I’m eager to grow into a more advanced role where I can solve real-world problems and build impactful software solutions.

\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Computer Science}, BRAC University \hfill {2018 - 2023}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Language Skills & Javascript, Java, Dart, Html, CSS\\
Framework Skills & React, Next, Express, SpringBoot\\
Database Skills & MongoDB, SQL, Firebase\\
Soft Skills & Problem-Solving, Presentation Skills, Flexibility\\

\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Fullstack Developer} \hfill August 2023 – Present\\
Vista Systech

As a Fullstack Developer at Vista Systech, I contributed to several production-ready applications across diverse industries. My responsibilities included building dynamic frontend interfaces with React, integrating APIs, and occasionally working on backend features. I also played a key role in projects within the BetterThat ecosystem, where I handled frontend development for multiple platforms and contributed to backend services involving AI agents and Meta Graph API integration.




 
% \textbf{Intern} \hfill Jun 2022 - Sept 2022\\
% Food Panda \hfill \textit{Food Panda Headquarters, Bangladesh}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Achieved Presentation skill by performing On boarding procedures.
%      \item Developed flexibility by working from home in turbulent times.
%      \item Gained experience in team work.
     
%  \end{itemize}


 
\textbf{Web Developer} \hfill May 2024 - August 2024\\
ANA-Soft 

As a Web Developer at ANA-Soft, I have worked extensively with ASP.NET to develop and maintain several dynamic websites, including the \href{https://ugc-equivalence.website-link.info/Login.aspx}{UGC} Equivalence portal. My role involved both back-end and front-end development, focusing on enhancing functionality, performance, and user experience. 

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Evocart} – \href{https://apple.nazarahnaturals.com/}{Evocart} \\
Developed subdomain-specific layout logic, implemented responsive UI updates, and handled API integrations.
Implemented AI agent functionality, integrat ed \textbf{Meta Graph API}, and exposed RESTful APIs for frontend usage.

\item \textbf{AI Agent} \\
Developed an \textbf{AI Agent} integrating Monica's API to analyze product images from URLs, extracting or generating product names and crafting concise descriptions. This enhanced the user experience by automating product identification and information retrieval.
\href{https://github.com/rafidrahman1/ai_agent}{(Git)}

\item \textbf{Meta Post} \\
Developed a \textbf{React} application integrating \textbf{Meta's Graph API}, enabling users to authenticate and seamlessly publish content to their Facebook Pages and associated Instagram accounts, thereby streamlining cross-platform social media management.
\href{https://github.com/rafidrahman1/meta_post}{(Git)}

\item \textbf{SewingTex React Conversion} – \href{https://sewingtexapparels.com/}{SewingTex} \\
Converted a complete \textbf{HTML}-based website to a React SPA with integrated \textbf{API}s for dynamic content rendering.

\item \textbf{WhatsApp Bulk Messenger} \\
Developed a fullstack messaging tool. Implemented logout and message history functionality, along with a responsive and clean UI design.

\item \textbf{BetterThat Ecosystem Projects} \\
Worked on multiple production-grade \textbf{React} applications under the BetterThat umbrella as a frontend developer. Responsibilities included building dynamic interfaces and full \textbf{API} integrations.
\begin{itemize}
    \item \href{https://ffc.betterthatconnect.com/}{Food for Change}
    \item \href{https://fig.betterthatconnect.com/}{Fishing in Godzone}
    \item \href{https://ditybit.com/}{Ditybit Auctions}
    \item \href{https://ar.betterthatconnect.com/}{Auckland Rescue}
\end{itemize}


\item \textbf{Physics Department, BUET} – \href{https://phy.buet.ac.bd/}{phy.buet.ac.bd} \\
Enhanced parts of the departmental website by making static components dynamic, improving maintainability and UX.
\end{rSection}


%----------------------------------------------------------------------------------------




\end{document}
